---
title: "Plotting Distributions"
author: "Ruixin"
date: "May 28, 2017"
output: ioslides_presentation
---

## Shiny Application With Plots
Using the Shiny package in R, we have created an application where you can see the different common distributions repsented in a diagram. The distributions you can look at are:

- Normal
- Uniform
- Log Normal
- Exponential

In the following slides, we will present our code and how we were able to build our Distribution Plot.

## ui.R - Part 1
To build out application, we need to write both a user interface(ui.R) and a server script (server.R). 

Please notice the use of the following functions in our code:

- numericInput() allows the user to enter any number
- radioButtons() allows the user tp select different modes
```{r, eval = FALSE}
library(shiny)
shinyUI(fluidPage(
  titlePanel("Plotting Distributions"),
    sidebarLayout(
    sidebarPanel(
      radioButtons("dist", "Distribution type:", c("Normal" = "norm", "Uniform" = "unif",
                     "Log-normal" = "lnorm", "Exponential" = "exp")),
      br(),
...
```

## ui.R - Part 2
```{r, eval = FALSE}
...
      numericInput("n", "How Many Random Numbers Should Be Plotted?", value = 1000, min = 1, 
                   max = 1000)
    ),
      mainPanel(
        h3("Distribution Plot"),
        plotOutput("plot"),
    ))
))
```

## server.R

```{r, eval=FALSE}
library(shiny)
shinyServer(function(input, output) {
    data <- reactive({
    dist <- switch(input$dist, norm = rnorm, unif = runif, lnorm = rlnorm, exp = rexp, rnorm)
    dist(input$n)
    })
    output$plot <- renderPlot({
    dist <- input$dist
    n <- input$n
    hist(data(), main=paste('r', dist, '(', n, ')', sep=''))
  })
})
```
