---
title: "Plotting Random Numbers in Shiny"
author: "Ruixin"
date: "May 25, 2017"
output: ioslides_presentation
---

## Shiny Application With Plots
Using the Shiny package in R, we have created a plot that can plot 1 to 1,000 random variables with a minimum of -100 and a maximum of 100 on both the x-axis and the y-axis. What is the use of this plot?

- False Positive Relationships
- Correlation vs. Causation
- Increased Date = Increased Information = Better Analysis

In the following slides, we will present our code and how we were able to build our Random Number Plot.

## ui.R - Part 1
To build out application, we need to write both a user interface(ui.R) and a server script (server.R). 

Please notice the use of the following functions in our code:

- numericInput() allows the user to enter any number
- checkboxInput() creates boxes that can be checked 
- plotOutput() displays a plot
- sliderInput() allows the user to define the min. and max of the axis
```{r, eval = FALSE}
library(shiny)
shinyUI(fluidPage(
  titlePanel("Creating Data Products With Shiny"),
  sidebarLayout(
    sidebarPanel(
...
```

## ui.R - Part 2
```{r, eval = FALSE}
...
      numericInput("numeric", "How Many Random Numbers Should Be Plotted?",
                   value = 1000, min = 1, max = 1000, step = 1),
      sliderInput("sliderX", "Pick Minimum and Maximum X Values",
                  -100, 100, value = c(-50, 50)),
      sliderInput("sliderY", "Pick Minimum and Maximum Y Values",
                  -100, 100, value = c(-50, 50)),
      checkboxInput("show_xlab", "Show/Hide X Axis Label", value = TRUE),
      checkboxInput("show_ylab", "Show/Hide Y Axis Label", value = TRUE),
      checkboxInput("show_title", "Show/Hide Title")
    ),
    mainPanel(
        h3("Graph of Random Points"),
        plotOutput("plot1")
    )
  )
))
```

## server.R

```{r}
library(shiny)
shinyServer(function(input, output){
  output$plot1 <- renderPlot({
    set.seed(2017-05-25)
    number_of_points <- input$numeric
    minX <- input$sliderX[1]
    maxX <- input$sliderX[2]
    minY <- input$sliderX[1]
    maxY <- input$sliderX[2]
    dataX <- runif(number_of_points, minX, maxX)
    dataY <- runif(number_of_points, minY, maxY)
    xlab <- ifelse(input$show_xlab, "X Axis", "")
    ylab <- ifelse(input$show_xlab, "Y Axis", "")
    main <- ifelse(input$show_title, "Title", "")
    plot(dataX, dataY, xlab = xlab, ylab = ylab, main = main,
         xlim = c(-100, 100), ylim = c(-100, 100))
  })
})
```
